\documentclass{article}
\usepackage{verbatim}
\usepackage{amsmath}
\usepackage{hyperref}
\usepackage{color}
\newcommand{\red}[1]{{\color{red}{#1}}}

\usepackage[a4paper,
            bindingoffset=0.2in,
            left=1.0in,
            right=1.0in,
            top=1.0in,
            bottom=1.0in,
            footskip=.25in]{geometry}

\title{Workflow Documentation}
\author{Caleb Kennedy Hill}
\date{Summer 2026}

\begin{document}

\maketitle

Things to do:
\red{
    \begin{itemize}
        \item Upload this to GitHub in the NEMS repo
        \item Start pipeline docs
        \item Start metrics metadata
        \item Expand ArcGIS Portfolio docs
    \end{itemize}
}

This document is intended to serve as a reference for those of us working on the UNH 
Sustainability Institute's Split Incentive Tak Force.


\section{Data Pipeline}\label{sec:pipeline}

This section will serve as documentation for the data pipeline.







%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%








\section{ArcGIS Online}
The goal of this section is to detail the process of turning \verb|.shp| files derived from \verb|GeoDataFrame|
into ArcGIS Instant Apps, for use in Portfolio projects.
The system schematic is as follows:
\[
\text{Portfolio} \longleftarrow 
\text{Instant App} \longleftarrow 
\text{Web Map} \longleftarrow 
\text{Feature Layer} 
\]



\subsection*{Create a Web App}
A \textbf{Portfolio} is a collection of \textbf{sections} which link to Web Apps.
We will be tying into the efforts of and extending the work of BU's CELT program.
With this in mind, our propotypical example of a Portfolio should be their Legacy Transition Atlas,
which is linked 
\href{https://bucas.maps.arcgis.com/apps/instant/portfolio/index.html?appid=ea07ae399445465e9dd2448f211affc0}{
    here
}.




\begin{enumerate}

    \item 
    Prepare ShapeFiles.
    Be sure that the relevant \verb|GeoDataFrame| has been exported and compressed into a \verb|.zip| file.
    The process of obtaining the shapefiles is outlined in Section~\ref{sec:pipeline}.

    \item
    Upload the \verb|.zip| file to ArcGIS Online as a \textbf{Feature Layer}.
    Navigate to the \verb|Content| tab of ArcGIS Online, then click \verb|New item|.
    Click the \verb|Feature layer|, and then the \verb|Upload a file| otpions.
    Be sure to choose the upload option that creates a Hosted Feature Layer.
    Pick a good name, and add a helpful description.

    \item 
    Back in the \verb|Content| window, open the Hosted Feature Layer you just created.
    Choose the option to \verb|Open in Map Viewer| in the upper right.

    \item 
    Fiddle and Save.
    The righthand side of the screen has a menu for changing how the map looks. 
    We don't yet have a standardized way to approach this, so for now just do what you
    think is reasonable.
    When you're done, click \verb|Save as| from the lefthand menu and pick the same name
    you used for the Feature Layer; add a short description as well.

    \item 
    In the \verb|Content| window, open Web Map.
    In the options on the right, click \verb|Create app| and choose \verb|Instant App|.
    In the page that opens, choose the \verb|Basic (Media Map)| option.
    Name it the same thing as the previous two.

    \item 
    In \verb|Step 1| of the following screen, add the map you created in the previous step.
    Make sure a legend is made available in \verb|Step 2|.
    So far, not much else has been standardized, so play around and pick something
    that doesn't seem crazy.

    \item 
    Before publishing, change the \verb|Share| settings on the lefthand menu to public.
    Then Publish the app.

\end{enumerate}






\subsection*{Create a Portfolio}
A portfolio is the housing for several different Instant Apps.

\[
\text{Portfolio} \longleftarrow 
\text{Instant App} \longleftarrow 
\text{Web Map} \longleftarrow 
\text{Feature Layer} 
\]

\begin{enumerate}

    
\item 
Create sections.


\item 
Upload base map for each section.


\item 
Put links to other apps in descriptopn.

\end{enumerate}




%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%






\end{document}